---
title: "Color Rule Kid - Norming Data"
author: "Anonymized for peer review"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    code_folding: hide
    toc: true
    toc_depth: 3
    toc_float: true
---

```{r setup, include=FALSE}
#knitr::opts_chunk$set(echo = TRUE)
library(knitr)
knitr::opts_chunk$set(
                prompt  = FALSE,
                cache   = FALSE,
                echo = TRUE,
                warning=F,
                message=F)
set.seed(1025) #set seed (only relevant for jittering of data points in plots)

```

```{r load packages and data, include=FALSE}
source(here::here("summarizeData.R"))
library(here)
library(tidyverse)
library(cowplot)
library(lme4)
library(car)
library(lmerTest)
library(janitor)
library(ggpirate)
library(jsonlite)
library(BayesFactor)
theme_set(theme_cowplot())
library(effectsize)
#source(here::here("summarizeData_new.R"))
```

Summarizes the results from a color discriminability norming study reported in the paper “Nameability Supports Rule-based Category Learning in Children and Adults” (authors removed, 2023).

# Read in and processing data {.tabset}

```{r cars}
kn_data <- read_csv(here::here("..","data","processed_data","ckn_v1_processed.csv")) %>%
  mutate(age_group="children")
an_data <- read_csv(here::here("..","data","processed_data","can_v1_processed.csv")) %>%
  mutate(age_group="adults")

#read in the color discriminability data from Zettersten & Lupyan (2020)
color_properties_zl <- read_csv(here::here("..","data","processed_data","color_properties.csv")) %>%
  filter(colorSet=="colorset1")
colorpair_discrim_rt_zl <- read_csv(here::here("..","data","processed_data","color_properties_discriminability.csv")) %>%
  filter(colorSet=="colorset1") %>%
  rename(zl_average_rt=average_rt) %>%
  mutate(
    pair = case_when(
      colorPair=="bluebrown" ~ "blue - brown"
    )
  )

kn_subj <- read_csv(here::here("..","data","subj_data","ckn_subjlog_anonymized.csv")) %>%
  clean_names()

kn_data <- kn_data %>%
  left_join(kn_subj,by=c("subject_id"="participant_id"))
```

## Read demographics

```{r}
kn_demographics <- read_csv(here::here("..","data","processed_data","colorrulekid_demographics.csv")) %>%
  clean_names() %>%
  rename(subject_id=participant_id) %>%
  mutate(age_months=as.numeric(age_months)) %>%
  mutate(
    gender = case_when(
      gender==0 ~ "female",
      gender==1 ~ "male",
      TRUE ~ NA_character_),
    race = case_when(
      race==1 ~ "American Indian or Alaska Native",
      race==2 ~ "Asian",
      race==3 ~ "Black or African American",
      race==4 ~ "Native Hawaiian or Other Pacific Islander",
      race==5 ~ "White",
      race==6 ~ "More than one race",
      race==7 ~ "Prefer not to disclose",
      TRUE ~ NA_character_
    ),
    ethnicity=case_when(
      ethnicity == 1 ~ "Hispanic or Latino",
      ethnicity == 2 ~ "Not Hispanic or Latino",
      ethnicity == 3 ~ "Prefer not to disclose",
      TRUE ~ NA_character_
    ),
    parental_education_category = case_when(
      parental_education == 1 ~ "Some high school",
       parental_education == 2 ~ "High school graduate", 
       parental_education == 3 ~ "Some college", 
       parental_education == 4 ~ "Trade/technical/vocational training", 
       parental_education == 5 ~ "College graduate",
      parental_education == 6 ~ "Postgraduate",
      parental_education == 7 ~ "Prefer not to disclose"
    ),
    household_income_category = case_when(
      home_income == 1 ~ "less than $24,999",
       home_income == 2 ~ "$25,000 to $49,999", 
       home_income == 3 ~ "$50,000 to 99,999", 
       home_income == 4 ~ "$100,000 or more", 
       home_income == 5 ~ "Prefer not to disclose"
    ))
an_demographics <- read_csv(here::here("..","data","processed_data","colorruleadults_demographics.csv")) %>%
  clean_names()%>%
  rename(subject_id=participant_id)%>%
  mutate(age=as.numeric(age)) %>%
  mutate(
    gender = case_when(
      gender==0 ~ "female",
      gender==1 ~ "male",
      TRUE ~ NA_character_),
    race = case_when(
      race==1 ~ "American Indian or Alaska Native",
      race==2 ~ "Asian",
      race==3 ~ "Black or African American",
      race==4 ~ "Native Hawaiian or Other Pacific Islander",
      race==5 ~ "White",
      race==6 ~ "More than one race",
      race==7 ~ "Prefer not to disclose",
      TRUE ~ NA_character_
    ),
    ethnicity=case_when(
      ethnicity == 1 ~ "Hispanic or Latino",
      ethnicity == 2 ~ "Not Hispanic or Latino",
      ethnicity == 3 ~ "Prefer not to disclose",
      TRUE ~ NA_character_
    ),
    parental_education_category = case_when(
      parental_education == 1 ~ "Some high school",
       parental_education == 2 ~ "High school graduate", 
       parental_education == 3 ~ "Some college", 
       parental_education == 4 ~ "Trade/technical/vocational training", 
       parental_education == 5 ~ "College graduate",
      parental_education == 6 ~ "Postgraduate",
      parental_education == 7 ~ "Prefer not to disclose"
    ),
    household_income_category = case_when(
      home_income == 1 ~ "less than $24,999",
       home_income == 2 ~ "$25,000 to $49,999", 
       home_income == 3 ~ "$50,000 to 99,999", 
       home_income == 4 ~ "$100,000 or more", 
       home_income == 5 ~ "Prefer not to disclose"
    ))
```

## Processing data

```{r}
kn_data <- kn_data %>%
  rowwise() %>%
  mutate(pair = paste(sort(c(target, foil)), collapse = " - "),colorPair=paste(sort(c(target, foil)), collapse = "")) %>%
  ungroup() %>%
  left_join(kn_demographics) %>%
  mutate(
    condition_c=case_when(
      condition=="high nameability" ~ 0.5,
      condition=="low nameability" ~ -0.5,
      TRUE ~ NA
    )
  )

an_data <- an_data %>%
  rowwise() %>%
  mutate(pair = paste(sort(c(target, foil)), collapse = " - "),colorPair=paste(sort(c(target, foil)), collapse = "")) %>%
  ungroup() %>%
  left_join(an_demographics)%>%
  mutate(
    condition_c=case_when(
      condition=="high nameability" ~ 0.5,
      condition=="low nameability" ~ -0.5,
      TRUE ~ NA
    )
  )
```

## Exclude participants

```{r}
kn_data <- kn_data %>%
  filter(exclude=="n")
#excluding the following participants
#exclude_participants <- c("CKN_101","CKN_112","CKN_114a","CKN_121","CKN_126","CKN_120")
```

# Demographics {.tabset}

## Children {.tabset}

### Age, Gender

```{r, message=F, warning=F}
####summarize by subject####
kid_subj <- kn_data %>%
  select(subject_id,age_months,gender,race, ethnicity,language_history,household_income_category,parental_education_category,family_history_color_blindness,color_blindness_dx) %>%
  distinct()

####summarize demographics####
kid_demographics <-  kid_subj %>%
  ungroup() %>%
  summarize(N=n(), 
            mean_age = round(mean(age_months,na.rm=TRUE),1), 
            sd_age = round(sd(age_months,na.rm=TRUE),1), 
            min_age = min(age_months,na.rm=TRUE), 
            max_age = max(age_months,na.rm=TRUE),
            count_female = sum(gender=='female',na.rm=TRUE),
            english_l1=paste(100*sum(str_detect(language_history,"1"))/sum(language_history!=""),"%",sep=""),
            bilingual=sum(language_history!="1"&language_history!="")
            )
kable(kid_demographics)
```

### Race

```{r, message=F, warning=F}
kid_subj %>%
  group_by(race) %>%
  summarize(count=n(),
            percent=count/nrow(kid_subj)) %>%
  kable()
```

### Ethnicity

```{r, message=F, warning=F}
kid_subj %>%
  group_by(ethnicity) %>%
  summarize(count=n(),
            percent=count/nrow(kid_subj)) %>%
  kable()
```

### Household Income

```{r, message=F, warning=F}
kid_subj %>%
  mutate(household_income_category = factor(household_income_category,levels=c("$100,000 or more","$50,000 to 99,999","$25,000 to $49,999","less than $24,999","Prefer not to disclose"))) %>%
  group_by(household_income_category) %>%
  summarize(count=n(),
            percent=count/nrow(kid_subj)) %>%
  kable()
```

### Parental Education

```{r, message=F, warning=F}
kid_subj %>%
  mutate(parental_education_category = factor(parental_education_category,levels=c("Some high school","High school graduate","Some college","Trade/technical/vocational training","College graduate","Postgraduate","Prefer not to disclose"))) %>%
  group_by(parental_education_category) %>%
  summarize(count=n(),
            percent=count/nrow(kid_subj)) %>%
  kable()
```

## Adults {.tabset}

### Age, Gender

```{r, message=F, warning=F}
####summarize by subject####
adult_subj <-  an_data %>%
  select(subject_id,age,gender,race, ethnicity,language_history,family_history_color_blindness,color_blindness_dx) %>%
  distinct()
####summarize demographics####
adult_demographics <-  adult_subj %>%
  ungroup() %>%
  summarize(N=n(), 
            mean_age = round(mean(age,na.rm=TRUE),1), 
            sd_age = round(sd(age,na.rm=TRUE),1), 
            min_age = min(age,na.rm=TRUE), 
            max_age = max(age,na.rm=TRUE),
            count_female = sum(gender=='female'),
            english_l1=paste(100*sum(str_detect(language_history,"1"))/sum(language_history!=""),"%",sep=""),
            bilingual=sum(language_history!="1"&language_history!=""))
kable(adult_demographics)
```

### Race

```{r, message=F, warning=F}
adult_subj %>%
  group_by(race) %>%
  summarize(count=n(),
            percent=count/nrow(kid_subj)) %>%
  kable()
```

### Ethnicity

```{r, message=F, warning=F}
adult_subj %>%
  group_by(ethnicity) %>%
  summarize(count=n(),
            percent=count/nrow(kid_subj)) %>%
  kable()
```

# Single-color analysis {.tabset}

These analyses are similar in structure to the analyses of color norming data in Zettersten & Lupyan (2020). We compute average reaction times (for correct trials only) and accuracies for each individual color, averaging across participants and foil pairings.

## Reaction Times

### Children {.tabset}

```{r}
# participant reaction times for each color
kid_participant_color_rt <- kn_data %>%
  filter(correct==1&condition!="practice"&rt<=5000&rt>=200) %>%
  group_by(subject_id,condition,target) %>% 
  summarize(
    N=sum(!is.na(rt)),
    avg_rt=mean(rt,na.rm=T)
  )

#average reaction times for each color
kid_color_rt <- kid_participant_color_rt %>%
  ungroup() %>%
  select(-N) %>%
  summarySEwithin("avg_rt",withinvars=c("condition","target"),idvar="subject_id",na.rm=TRUE)

#join with color property data (from Zettersten & Lupyan, 2020)
kid_color_rt <- kid_color_rt %>%
  left_join(
    color_properties_zl,by=join_by(target==colorName)
  )
```

#### Plot

```{r}
kid_color_rt <- kid_color_rt %>%
  mutate(
    target_label = case_when(
      target=="red" ~ "(220, 20, 0) - red",
    target=="brown"~"(120, 80, 40) - brown",
    target=="blue"~"(30, 90, 210) - blue",
    target=="yellow"~"(250, 240, 0) - yellow",
    target=="purple"~"(130, 30, 180) - purple",
    target=="orange"~"(250, 120, 30) - orange",
    target=="pink"~"(200, 170, 170) - mauve",
    target=="mustard"~"(170, 160, 40) - chartreuse",
    target=="turquoise"~"(150, 200, 180) - turquoise",
    target=="neonyellow"~"(220, 240, 150) - honeydew",
    target=="darkgreenblue"~"(70, 100, 90) - teal",
    target=="lightred"~"(200, 100, 70) - sienna")
  )
ggplot(kid_color_rt, aes(reorder(target_label,-avg_rt,mean),avg_rt, color=condition))+
  geom_bar(aes(fill=condition,alpha=condition),stat="identity",size=1.5, position=position_dodge(.95))+
  geom_errorbar(aes(ymin=avg_rt-ci,ymax=avg_rt+ci), width=0.3,size=1.2, position=position_dodge(.95))+
  #coord_cartesian(ylim=c(500,700))+
  #ggtitle("Child Discriminability")+
  ylab("Reaction Time (in ms)")+
  xlab("Color")+
  scale_color_brewer(palette="Set1",name="Nameability")+
  scale_fill_brewer(palette="Set1",name="Nameability")+
  scale_alpha_manual(name="Nameability",values=c(0,0.5))+
  theme_cowplot()+
  theme(legend.position=c(0.05,0.2),legend.background=element_rect(fill="white")) + 
  theme(axis.text.x  = element_text(angle=90, vjust=0.5),plot.title = element_text(hjust = 0.5))+
  theme(text=element_text(size=18))+
  theme(strip.text.x = element_text(size=16), plot.background = element_rect(fill="white",color="white"))
ggsave(here::here("figures","kid_color_rt.png"),width=9, height=6,dpi=600)
```

#### Overall Results

Evaluating whether high nameability colors and low nameability colors differ in their average discriminability (RT-based)

```{r}
#overall average
kid_color_rt %>%
  group_by(condition) %>%
  summarize(
    N = n(),
    mean_rt = mean(avg_rt),
    sd = sd(avg_rt),
    ci = qt(0.975, N-1)*sd/sqrt(N),
    lower_ci = mean_rt-ci,
    upper_ci = mean_rt+ci
  ) %>%
  kable()

# t-test
t.test(avg_rt ~ condition, data = kid_color_rt, paired = FALSE)

#Bayes Factor
#evidence for the null hypothesis
1/ttestBF(kid_color_rt$avg_rt[kid_color_rt$condition=="high nameability"],kid_color_rt$avg_rt[kid_color_rt$condition=="low nameability"],paired=TRUE)
```

### Adults {.tabset}

```{r}
# participant reaction times for each color
adult_participant_color_rt <- an_data %>%
  filter(correct==1&condition!="practice"&rt<=2000&rt>=200) %>%
  group_by(subject_id,condition,target) %>% 
  summarize(
    N=sum(!is.na(rt)),
    avg_rt=mean(rt,na.rm=T)
  )

#average reaction times for each color
adult_color_rt <- adult_participant_color_rt %>%
  ungroup() %>%
  select(-N) %>%
  summarySEwithin("avg_rt",withinvars=c("condition","target"),idvar="subject_id",na.rm=TRUE)

#join with color property data (from Zettersten & Lupyan, 2020)
adult_color_rt <- adult_color_rt %>%
  left_join(
    color_properties_zl,by=join_by(target==colorName)
  )
```

#### Plot

```{r}
adult_color_rt <- adult_color_rt %>%
  mutate(
    target_label = case_when(
      target=="red" ~ "(220, 20, 0) - red",
    target=="brown"~"(120, 80, 40) - brown",
    target=="blue"~"(30, 90, 210) - blue",
    target=="yellow"~"(250, 240, 0) - yellow",
    target=="purple"~"(130, 30, 180) - purple",
    target=="orange"~"(250, 120, 30) - orange",
    target=="pink"~"(200, 170, 170) - mauve",
    target=="mustard"~"(170, 160, 40) - chartreuse",
    target=="turquoise"~"(150, 200, 180) - turquoise",
    target=="neonyellow"~"(220, 240, 150) - honeydew",
    target=="darkgreenblue"~"(70, 100, 90) - teal",
    target=="lightred"~"(200, 100, 70) - sienna")
  )
ggplot(adult_color_rt, aes(reorder(target_label,-avg_rt,mean),avg_rt, color=condition))+
  geom_bar(aes(fill=condition,alpha=condition),stat="identity",size=1.5, position=position_dodge(.95))+
  geom_errorbar(aes(ymin=avg_rt-ci,ymax=avg_rt+ci), width=0.3,size=1.2, position=position_dodge(.95))+
  #coord_cartesian(ylim=c(500,700))+
  #ggtitle("Adult Discriminability")+
  ylab("Reaction Time (in ms)")+
  xlab("Color")+
  scale_color_brewer(palette="Set1",name="Nameability")+
  scale_fill_brewer(palette="Set1",name="Nameability")+
  scale_alpha_manual(name="Nameability",values=c(0,0.5))+
  theme_cowplot()+
  theme(legend.position=c(0.05,0.2),legend.background=element_rect(fill="white")) + 
  theme(axis.text.x  = element_text(angle=90, vjust=0.5),plot.title = element_text(hjust = 0.5))+
  theme(text=element_text(size=18))+
  theme(strip.text.x = element_text(size=16), plot.background = element_rect(fill="white",color="white"))
ggsave(here::here("figures","adult_color_rt.png"),width=9, height=6,dpi=600)
```


#### Overall Results

Evaluating whether high nameability colors and low nameability colors differ in their average discriminability (RT-based)

```{r}
#overall average
adult_color_rt %>%
  group_by(condition) %>%
  summarize(
    N = n(),
    mean_rt = mean(avg_rt),
    sd = sd(avg_rt),
    ci = qt(0.975, N-1)*sd/sqrt(N),
    lower_ci = mean_rt-ci,
    upper_ci = mean_rt+ci
  ) %>%
  kable()

# t-test
t.test(avg_rt ~ condition, data = adult_color_rt, paired = FALSE)

#Bayes Factor
#evidence for the null hypothesis
1/ttestBF(adult_color_rt$avg_rt[adult_color_rt$condition=="high nameability"],adult_color_rt$avg_rt[adult_color_rt$condition=="low nameability"],paired=TRUE)
```

### Correlations {.tabset}

```{r}
adult_color_rt_to_join <- adult_color_rt %>%
  select(target,avg_rt) %>%
  rename(adult_avg_rt=avg_rt)
kid_color_rt <- kid_color_rt %>%
  left_join(adult_color_rt_to_join)

ggplot(kid_color_rt,aes(avg_rt,adult_avg_rt))+
  geom_point(aes(color=condition))+
  geom_smooth(method="lm")+
  xlab("Average Color Reaction Time (ms) - Children")+
  ylab("Average Color Reaction Time (ms) - Adults")+
  theme(legend.position=c(0.1,0.2))
```

```{r}
#Correlations
cor.test(
  kid_color_rt$avg_rt,
  kid_color_rt$adult_avg_rt,
)
```

## Accuracy {.tabset}

### Children {.tabset}

```{r}
# participant accuracy for each color
kid_participant_color_acc <- kn_data %>%
  filter(condition!="practice") %>%
  group_by(subject_id,condition,target) %>% 
  summarize(
    N=sum(!is.na(correct)),
    avg_accuracy=mean(correct,na.rm=T)
  )

#average accuracy for each color
kid_color_acc <- kid_participant_color_acc %>%
  ungroup() %>%
  select(-N) %>%
  summarySEwithin("avg_accuracy",withinvars=c("condition","target"),idvar="subject_id",na.rm=TRUE)
```

Evaluating whether high nameability colors and low nameability colors differ in their average accuracy

```{r}
#overall average
kid_color_acc %>%
  group_by(condition) %>%
  summarize(
    N = n(),
    mean_accuracy = mean(avg_accuracy),
    sd = sd(avg_accuracy),
    ci = qt(0.975, N-1)*sd/sqrt(N),
    lower_ci = mean_accuracy-ci,
    upper_ci = mean_accuracy+ci
  ) %>%
  kable()

# t-test
t.test(avg_accuracy ~ condition, data = kid_color_acc, paired = FALSE)

#Bayes Factor
#evidence for the null hypothesis
1/ttestBF(kid_color_acc$avg_accuracy[kid_color_acc$condition=="high nameability"],kid_color_acc$avg_accuracy[kid_color_acc$condition=="low nameability"],paired=TRUE)
```

### Adults {.tabset}

```{r}
# participant accuracy for each color
adult_participant_color_acc <- an_data %>%
  filter(condition!="practice") %>%
  group_by(subject_id,condition,target) %>% 
  summarize(
    N=sum(!is.na(correct)),
    avg_accuracy=mean(correct,na.rm=T)
  )

#average accuracy for each color
adult_color_acc <- adult_participant_color_acc %>%
  ungroup() %>%
  select(-N) %>%
  summarySEwithin("avg_accuracy",withinvars=c("condition","target"),idvar="subject_id",na.rm=TRUE)
```

Evaluating whether high nameability colors and low nameability colors differ in their average accuracy

```{r}
#overall average
adult_color_acc %>%
  group_by(condition) %>%
  summarize(
    N = n(),
    mean_accuracy = mean(avg_accuracy),
    sd = sd(avg_accuracy),
    ci = qt(0.975, N-1)*sd/sqrt(N),
    lower_ci = mean_accuracy-ci,
    upper_ci = mean_accuracy+ci
  ) %>%
  kable()

# t-test
t.test(avg_accuracy ~ condition, data = adult_color_acc, paired = FALSE)

#Bayes Factor
#evidence for the null hypothesis
1/ttestBF(adult_color_acc$avg_accuracy[adult_color_acc$condition=="high nameability"],adult_color_acc$avg_accuracy[adult_color_acc$condition=="low nameability"],paired=TRUE)
```

# Color Pair Analysis {.tabset}

## Children {.tabset}

```{r}
# participant reaction times for each color pair
kid_participant_color_pair_rt <- kn_data %>%
  filter(correct==1&condition!="practice"&rt<=5000&rt>=200) %>%
  group_by(subject_id,condition,pair,colorPair) %>% 
  summarize(
    N=sum(!is.na(rt)),
    avg_rt=mean(rt,na.rm=T)
  )

color_pairing <- kid_participant_color_pair_rt %>%
  ungroup() %>%
  select(pair,colorPair) %>%
  distinct()

#average reaction times for each color
kid_color_pair_rt <- kid_participant_color_pair_rt %>%
  ungroup() %>%
  select(-N) %>%
  summarySEwithin("avg_rt",withinvars=c("condition","pair"),idvar="subject_id",na.rm=TRUE) %>%
  left_join(color_pairing)

#join with color property data (from Zettersten & Lupyan, 2020)
kid_color_pair_rt <- kid_color_pair_rt %>%
  left_join(
    select(colorpair_discrim_rt_zl,colorPair,zl_average_rt,dE2000)
  ) %>%
  mutate(group="children")
```

### Plot

```{r}
ggplot(kid_color_pair_rt, aes(reorder(pair,-avg_rt,mean),avg_rt, color=condition))+
  geom_bar(aes(fill=condition,alpha=condition),stat="identity",size=1.5, position=position_dodge(.95))+
  geom_errorbar(aes(ymin=avg_rt-ci,ymax=avg_rt+ci), width=0.3,size=1.2, position=position_dodge(.95))+
  #coord_cartesian(ylim=c(500,700))+
  #ggtitle("Child Discriminability")+
  ylab("Reaction Time (in ms)")+
  xlab("Color Pair")+
  scale_color_brewer(palette="Set1",name="Nameability")+
  scale_fill_brewer(palette="Set1",name="Nameability")+
  scale_alpha_manual(name="Nameability",values=c(0,0.5))+
  theme(legend.position=c(0.05,0.2),legend.background=element_rect(fill="white")) + 
  theme(axis.text.x  = element_text(angle=90, vjust=0.5),plot.title = element_text(hjust = 0.5))
ggplot(kid_color_pair_rt, aes(condition,avg_rt, color=condition))+
  geom_boxplot()+
  geom_jitter(width=0.1)+
  xlab("Condition")+
  theme(legend.position="none")+
  ylab("Average Reaction Time (in ms)")+
  scale_color_brewer(palette="Set1",name="Nameability")
```

### Overall Results

Evaluating whether high nameability colors and low nameability colors differ in their average discriminability (RT-based)

```{r}
#overall average
kid_color_pair_rt %>%
  group_by(condition) %>%
  summarize(
    N = n(),
    mean_rt = mean(avg_rt),
    sd = sd(avg_rt),
    ci = qt(0.975, N-1)*sd/sqrt(N),
    lower_ci = mean_rt-ci,
    upper_ci = mean_rt+ci
  ) %>%
  kable()

# t-test
t.test(avg_rt ~ condition, data = kid_color_pair_rt, paired = FALSE)

#Bayes Factor
#evidence for the null hypothesis
1/ttestBF(kid_color_pair_rt$avg_rt[kid_color_pair_rt$condition=="high nameability"],kid_color_pair_rt$avg_rt[kid_color_pair_rt$condition=="low nameability"],paired=TRUE)
```

## Adults {.tabset}

```{r}
# participant reaction times for each color pair
adult_participant_color_pair_rt <- an_data %>%
  filter(correct==1&condition!="practice"&rt<=2000&rt>=200) %>%
  group_by(subject_id,condition,pair,colorPair) %>% 
  summarize(
    N=sum(!is.na(rt)),
    avg_rt=mean(rt,na.rm=T)
  )

color_pairing <- adult_participant_color_pair_rt %>%
  ungroup() %>%
  select(pair,colorPair) %>%
  distinct()

#average reaction times for each color
adult_color_pair_rt <- adult_participant_color_pair_rt %>%
  ungroup() %>%
  select(-N) %>%
  summarySEwithin("avg_rt",withinvars=c("condition","pair"),idvar="subject_id",na.rm=TRUE) %>%
  left_join(color_pairing)

#join with color property data (from Zettersten & Lupyan, 2020)
adult_color_pair_rt <- adult_color_pair_rt %>%
  left_join(
    select(colorpair_discrim_rt_zl,colorPair,zl_average_rt,dE2000)
  )%>%
  mutate(group="adults")
```

### Plot

```{r}
ggplot(adult_color_pair_rt, aes(reorder(pair,-avg_rt,mean),avg_rt, color=condition))+
  geom_bar(aes(fill=condition,alpha=condition),stat="identity",size=1.5, position=position_dodge(.95))+
  geom_errorbar(aes(ymin=avg_rt-ci,ymax=avg_rt+ci), width=0.3,size=1.2, position=position_dodge(.95))+
  #coord_cartesian(ylim=c(500,700))+
  #ggtitle("Adult Discriminability")+
  ylab("Reaction Time (in ms)")+
  xlab("Color Pair")+
  scale_color_brewer(palette="Set1",name="Nameability")+
  scale_fill_brewer(palette="Set1",name="Nameability")+
  scale_alpha_manual(name="Nameability",values=c(0,0.5))+
  theme(legend.position=c(0.05,0.2),legend.background=element_rect(fill="white")) + 
  theme(axis.text.x  = element_text(angle=90, vjust=0.5),plot.title = element_text(hjust = 0.5))
ggplot(adult_color_pair_rt, aes(condition,avg_rt, color=condition))+
  geom_boxplot()+
  geom_jitter(width=0.1)+
  xlab("Condition")+
  theme(legend.position="none")+
  ylab("Average Reaction Time (in ms)")+
  scale_color_brewer(palette="Set1",name="Nameability")
```

### Overall Results

Evaluating whether high nameability colors and low nameability colors differ in their average discriminability (RT-based)

```{r}
#overall average
adult_color_pair_rt %>%
  group_by(condition) %>%
  summarize(
    N = n(),
    mean_rt = mean(avg_rt),
    sd = sd(avg_rt),
    ci = qt(0.975, N-1)*sd/sqrt(N),
    lower_ci = mean_rt-ci,
    upper_ci = mean_rt+ci
  ) %>%
  kable()

# t-test
t.test(avg_rt ~ condition, data = adult_color_pair_rt, paired = FALSE)

#Bayes Factor
#evidence for the null hypothesis
1/ttestBF(adult_color_pair_rt$avg_rt[adult_color_pair_rt$condition=="high nameability"],adult_color_pair_rt$avg_rt[adult_color_pair_rt$condition=="low nameability"],paired=TRUE)
```

## Correlations {.tabset}

### Kids vs. Adults
```{r}
color_pair_rt <- kid_color_pair_rt %>%
  bind_rows(adult_color_pair_rt)

color_pair_rt_wide <- color_pair_rt %>%
  select(-N,-se,-sd,-ci,-avg_rt_norm,-zl_average_rt,-dE2000,-colorPair) %>%
  pivot_wider(
    names_from="group",
    values_from="avg_rt"
  ) 

ggplot(color_pair_rt_wide, aes(children, adults))+
  geom_point()+
  geom_smooth(method="lm")

cor.test(
  color_pair_rt_wide$children,
  color_pair_rt_wide$adults,
)
```

# Main Linear Mixed-effects Model {.tabset}

## Children {.tabset}

### Reaction Time

We fit a trial-by-trial linear mixed effects model prediction reaction time from condition, including a by-participant random intercept and random slope for condition and a by-color-pair random intercept.

```{r}
kn_data <- kn_data %>%
  mutate(condition_c=ifelse(condition=="high nameability",0.5,-0.5))
m <- lmer(rt ~ condition_c+(1+condition_c|subject_id)+(1|pair),data=filter(kn_data,rt<=5000&correct==1&condition!="practice"))
summary(m)
```

Reaction times decline with age, but there is no interaction with condition

``` {r}
m <- lmer(rt ~ condition_c*age_months+(1+condition_c|subject_id)+(1|pair),data=filter(kn_data,rt<=5000&correct==1&condition!="practice"))
summary(m)
```

### Accuracy

We fit a trial-by-trial logistic mixed effects model prediction reaction time from condition, including a by-participant random intercept and random slope for condition and a by-color-pair random intercept.

```{r}
m <- glmer(correct ~ condition_c+(1+condition_c|subject_id)+(1|pair),data=filter(kn_data,rt<=5000&condition!="practice"),family="binomial")
summary(m)
```

No interaction between condition and age

```{r}
m <- glmer(correct ~ condition_c*age_months+(1+condition_c|subject_id)+(1|pair),data=filter(kn_data,rt<=5000&condition!="practice"),family="binomial",glmerControl(optimizer="bobyqa"))
summary(m)
```

## Adults {.tabset}

### Reaction Time 

We fit a trial-by-trial linear mixed effects model prediction reaction time from condition, including a by-participant random intercept and random slope for condition and a by-color-pair random intercept.

```{r}
an_data <- an_data %>%
  mutate(condition_c=ifelse(condition=="high nameability",0.5,-0.5))
m <- lmer(rt ~ condition_c+(1+condition_c|subject_id)+(1|pair),data=filter(an_data,rt<=2000&correct==1&condition!="practice"))
summary(m)
```

### Accuracy

We fit a trial-by-trial logistic mixed effects model prediction reaction time from condition, including a by-participant random intercept and random slope for condition and a by-color-pair random intercept.

```{r}
m <- glmer(correct ~ condition_c+(1+condition_c|subject_id)+(1|pair),data=filter(kn_data,rt<=2000&condition!="practice"),family="binomial",glmerControl(optimizer="bobyqa"))
summary(m)
```

## Child - Adult Interaction

We also found no significant interaction between age group and condition in a linear mixed-effects model.

```{r}
overall_data <- kn_data %>%
  select(-home_income,-parental_education,-family_history_color_blindness,-color_blindness_dx) %>%
  bind_rows(select(an_data,-home_income,-parental_education,-family_history_color_blindness,-color_blindness_dx)) %>%
  mutate(age_group_c=ifelse(age_group=="children",-0.5,0.5))
m <- lmer(rt~ condition_c*age_group_c+(1+condition_c|subject_id)+(1|pair),data=filter(overall_data,rt<=5000&correct==1&condition!="practice"))
summary(m)

```

# Relation with Zettersten & Lupyan (2020) norming data

## ZL discriminability - Single Color {.tabset}

### Children & ZL discriminability {.tabset}

#### Correlation Plot

```{r}
p1 <- ggplot(kid_color_rt,aes(avg_rt,rt_different))+
  geom_point(aes(color=condition))+
  geom_smooth(method="lm")+
  xlab("Average Color Reaction Time (ms) - Children")+
  ylab("Average Color Reaction Time (ms) - Different Trials\nZettersten & Lupyan (2020)")+
  theme(legend.position=c(0.1,0.2))

p2 <- ggplot(kid_color_rt,aes(avg_rt,rt_same))+
  geom_point(aes(color=condition))+
  geom_smooth(method="lm")+
  xlab("Average Color Reaction Time (ms) - Children")+
  ylab("Average Color Reaction Time (ms) - Same Trials\nZettersten & Lupyan (2020)")+
  theme(legend.position=c(0.1,0.2))

plot_grid(p1,p2)
```

#### Correlation - Different Trials
```{r}
#Correlations
cor.test(
  kid_color_rt$avg_rt,
  kid_color_rt$rt_different,
)
```

#### Correlation - Same Trials
```{r}
cor.test(
  kid_color_rt$avg_rt,
  kid_color_rt$rt_same,
)
```

### Adults & ZL discriminability {.tabset}

#### Correlation Plot

```{r}
p1 <- ggplot(adult_color_rt,aes(avg_rt,rt_different))+
  geom_point(aes(color=condition))+
  geom_smooth(method="lm")+
  xlab("Average Color Reaction Time (ms) - Adults")+
  ylab("Average Color Reaction Time (ms) - Different Trials\nZettersten & Lupyan (2020)")+
  theme(legend.position=c(0.1,0.2))

p2 <- ggplot(adult_color_rt,aes(avg_rt,rt_same))+
  geom_point(aes(color=condition))+
  geom_smooth(method="lm")+
  xlab("Average Color Reaction Time (ms) - Adults")+
  ylab("Average Color Reaction Time (ms) - Same Trials\nZettersten & Lupyan (2020)")+
  theme(legend.position=c(0.1,0.2))

plot_grid(p1,p2)
```

#### Correlation - Different Trials
```{r}
#Correlations
cor.test(
  adult_color_rt$avg_rt,
  adult_color_rt$rt_different,
)
```

#### Correlation - Same Trials
```{r}
cor.test(
  adult_color_rt$avg_rt,
  adult_color_rt$rt_same,
)
```

## ZL discriminability - Color Pairs {.tabset}

### Children & ZL discriminability {.tabset}

```{r}
ggplot(kid_color_pair_rt,aes(avg_rt,zl_average_rt))+
  geom_point(aes(color=condition,shape=condition),size=3)+
  geom_smooth(method="lm",color="black")+
  scale_color_brewer(palette = "Set1") +
  xlab("Average Color Reaction Time (ms) - Children")+
  ylab("Average Color Reaction Time (ms) - Color Pairs\nZettersten & Lupyan (2020)")+
  theme(legend.position=c(0.1,0.7))
```

```{r}
#Correlations
cor.test(
  kid_color_pair_rt$avg_rt,
  kid_color_pair_rt$zl_average_rt,
)
```

### Adults & ZL discriminability {.tabset}

```{r}
ggplot(adult_color_pair_rt,aes(avg_rt,zl_average_rt))+
  geom_point(aes(color=condition,shape=condition),size=3)+
  geom_smooth(method="lm",color="black")+
  scale_color_brewer(palette = "Set1") +
  xlab("Average Color Reaction Time (ms) - Children")+
  ylab("Average Color Reaction Time (ms) - Color Pairs\nZettersten & Lupyan (2020)")+
  theme(legend.position=c(0.1,0.8))+
  theme(text=element_text(size=18))+
  theme(strip.text.x = element_text(size=16), plot.background = element_rect(fill="white",color="white"))
ggsave(here::here("figures","adult_zl2020.png"),width=9, height=6,dpi=600)
```

```{r}
#Correlations
cor.test(
  adult_color_pair_rt$avg_rt,
  adult_color_pair_rt$zl_average_rt,
)
```

## deltaE 2000 {.tabset}

### Children & deltaE2000 {.tabset}

```{r}
ggplot(kid_color_pair_rt,aes(avg_rt,dE2000))+
  geom_point(aes(color=condition,shape=condition),size=3)+
  geom_smooth(method="lm",color="black")+
  scale_color_brewer(palette = "Set1") +
  xlab("Average Color Reaction Time (ms) - Children")+
  ylab("deltaE2000")+
  theme(legend.position=c(0.05,0.15))+
  theme(text=element_text(size=18))+
  theme(strip.text.x = element_text(size=16), plot.background = element_rect(fill="white",color="white"))
ggsave(here::here("figures","kid_dE2000.png"),width=9, height=6,dpi=600)
```

Children's reaction times correlated with deltaE2000 values.

```{r}
#Correlations
cor.test(
  kid_color_pair_rt$avg_rt,
  kid_color_pair_rt$dE2000,
)
```

### Adults & deltaE2000 {.tabset}

```{r}
ggplot(adult_color_pair_rt,aes(avg_rt,dE2000))+
  geom_point(aes(color=condition,shape=condition),size=3)+
  geom_smooth(method="lm",color="black")+
  scale_color_brewer(palette = "Set1") +
  xlab("Average Color Reaction Time (ms) - Adults")+
  ylab("deltaE2000")+
  theme(legend.position=c(0.6,0.8))+
  theme(text=element_text(size=18))+
  theme(strip.text.x = element_text(size=16), plot.background = element_rect(fill="white",color="white"))
ggsave(here::here("figures","adult_dE2000.png"),width=9, height=6,dpi=600)
```

Adults' reaction times correlated with deltaE2000 values.

```{r}
#Correlations
cor.test(
  adult_color_pair_rt$avg_rt,
  adult_color_pair_rt$dE2000,
)
```

### ZL discriminability (adults) & deltaE2000 {.tabset}

```{r}
ggplot(adult_color_pair_rt,aes(zl_average_rt,dE2000))+
  geom_point(aes(color=condition,shape=condition),size=3)+
  geom_smooth(method="lm",color="black")+
  scale_color_brewer(palette = "Set1") +
  xlab("Average Color Reaction Time (ms) - Adults\n(Zettersten & Lupyan (2020)")+
  ylab("deltaE2000")+
  theme(legend.position=c(0.7,0.8))
  
```

Adults' reaction times correlated with deltaE2000 values.

```{r}
#Correlations
cor.test(
  adult_color_pair_rt$zl_average_rt,
  adult_color_pair_rt$dE2000,
)
```

# Session Info

```{r}
sessionInfo()
```

